Preliminary Draft

### 2021-07-23 article/draft.tex
updates to code create_figures to include twitter lifesite

{\color{pink} What about something about recommendations ? authoritative content  }

>>>>

{\color{pink}

Youtube recommends content to the users based on the watch history and searchers they do in google and youtube. It is possible for the user to change the recommendation based on his preferences by removing videos from his history or by pausing the watch history. This type of system can influence what a user gets recommended in a negative way especially if the user is constantly watching misleading videos or conspiracy theory type of videos.  Youtube says that they set out to prevent their systems from serving up content that could misinform users in a harmful way, particularly in domains that rely on veracity, such as science, medicine, news, or historical events.  The way that youtube determines misinformation is by using external human evaluators and experts to examine if the video is promoting misleading information or conspiracy theories. Then using the feedback of the evaluators, they use machine learning systems to develop models that generate recommendations. The models work on reviewing videos daily to reduce the spread of misinformation.

To examine this effect, we designed an experiment that simulates user behavior in youtube using selenium library and python. The experiment starts with one misleading video identified by fact checkers and a clean watch history. Then the system collects the recommendation for this video and clicks on the top 10 recommendations in sequential order and collects their recommendations. The experiment is repeated for 65 misleading videos. In addition, to copy the user behavior, the system watches the videos for a couple of minutes to half of it. After the data collection, a fact checker examined the top 80 recommended videos (Videos that have been recommended many times during the experiment). The results showed little misinformation (less than 10\%) in the top recommendations. Therefore, this can be the result of youtube reducing the visibility of videos with misinformation or there is little misinformation in youtube or the experiment setup didn’t influence the recommendation engine behavior since we start with only one misleading video every time.

}
